Quasars Probing Quasars IX. Probing the Circumgalactic Flows of Quasars [v1.2]

### 2017-02-25 QPQ9/qpq9_draft.tex
added figure of monte carlo simulation

\begin{abstract}
Absorption-line analysis of the circumgalactic medium has traditionally been limited by the 
difficulty to distinguish between inflows and outflows. We examine the flows of gas in the 
environments of massive galaxies hosting quasars at $z\sim2$. We employ 195 projected quasar pairs 
to study the circumgalactic gas of the foreground quasars in absorption. The foreground quasars 
have precise redshift measurements with uncertainty $<400\,{\rm km\,s^{-1}}$. We stack the 
background quasar spectra at the foreground quasar's systemic redshift. The mean absorption in 
\ion{C}{2}, \ion{C}{4}, and \ion{Mg}{2} show large intrinsic velocity fields, and have velocity 
centroids that show a small positive offset relative to the systemic. We argue the results can be 
explained by outflowing gas combined with anisotropic or intermittent ionizing radiation of the 
quasars. 
\end{abstract}

@@

In this paper (hereafter QPQ9), we examine the flows of gas in the environments of massive 
galaxies hosting quasars. Our approach leverages a large dataset of quasar pairs 
\citep[][QPQ1]{QPQ1} to use the 
standard technique of absorption-line spectroscopy with background quasars. These quasar pairs 
have angular separations that correspond to less than 300\,kpc projected separation at the 
foreground quasar's redshift. Our previous publications from these quasar pairs have established 
that these galaxies are surrounded by a massive, cool, and enriched circumgalactic medium 
\citep[QPQ5, QPQ6, QPQ7:][]{QPQ5,QPQ6,QPQ7}. We have collected a sample of 195 background 
spectra that are paired with foreground quasars with precisely measured redshifts. Our primary 
scientific interests are twofold: (i) search for signatures of galactic-scale outflows from the 
central galaxy, presumably driven by recent star formation and/or active galactic nuclei feedback; 
(ii) characterize the dynamics of galactic flows around these massive system. We further describe 
an aspect of this experiment that offers a unique opportunity to study galactic flows: we argue 
that, the anisotropic or intermittent radiation of the foreground quasars breaks the symmetry in 
the velocity field of circumgalactic absorbers.

@@

\begin{figure}
\includegraphics[width=3in]{Figures/fig_experiment.pdf}
\caption{These panels summarize properties of the QPQ9 dataset. The QPQ survey selects 
quasar pairs of $R_\perp < 300$\,kpc and $z_{\rm fg}>1.6$. Assuming that the foreground quasars 
emit isotropically and at a distance equal to the impact parameter, the aenhancement in the UV 
flux relative to the extragalactic UV background, $g_{\rm UV}$, can be estimated. Large 
symbols correspond to foreground quasars with the most precise redshift measurement from 
[\ion{O}{3}]\,5007, while small symbols correspond to $z_{\rm fg}$ 
measurements from \ion{Mg}{2}\,2800, H$\alpha$, or H$\beta$ emission. The top panel shows 
quasar pairs with coverage of \ion{C}{2}\,1334 at $z_{\rm fg}$ in the background quasar spectra. 
The middle panel shows pairs with coverage of \ion{C}{4}\,1548. The bottom panel shows 
pairs with coverage of \ion{Mg}{2}\,2796. 
}
\label{fig:experiment}
\end{figure}

@@

From our QPQ survey\footnote{http://www.qpqsurvey.org}, we have analyzed a subset of systems that 
pass within transverse separation $R_\perp<300$\,kpc from a foreground quasar with 
$z_{\rm fg} > 1.6$. We restrict the sample to foreground quasars with redshift measured from 
\ion{Mg}{2}\,2800, [\ion{O}{3}]\,5007, H$\alpha$, or H$\beta$ emission, giving a precision of 
$400\,{\rm km\,s^{-1}}$ or better. 
[\ion{O}{3}] emission-line redshifts have the smallest dispersion of $44\,{\rm km\,s^{-1}}$ about 
the systemic redshift, and we analyze the sub-sample with [\ion{O}{3}] redshifts separately. 
The [\ion{O}{3}] line has an average blueshift of $27\,{\rm km\,s^{-1}}$ about the systemic 
redshift \citep{Boroson05}, which has been added when we compute the 
redshift of the line. Systemic redshifts measured from \ion{Mg}{2} have a precision of 
$272\,{\rm km\,s^{-1}}$, and we have taken into account the median redshift of 
$97\,{\rm km\,s^{-1}}$ of \ion{Mg}{2} from [\ion{O}{3}] \citep{Richards+02}. In QPQ8 
\citep{QPQ8}, we have quantified the precision of H$\alpha$ and H$\beta$ to be 
$300\,{\rm km\,s^{-1}}$ and $392\,{\rm km\,s^{-1}}$ respectively. We further add to the QPQ 
dataset with quasar pairs selected from the public dataset of 
igmspec\footnote{https://github.com/specdb/igmspec}, which includes the spectra from the quasar 
catalogs based upon the Sloan Digital Sky Survey Seventh Data Release \citep{Schneider+10} and the 
Twelfth Data Release \citep{Paris+17}. We 
only select pairs with $z_{\rm fg}$ measured by \cite{HewettWild10} using the \ion{Mg}{2}\,1800 
emission-line. We reached a final sample size of 195. Figure~\ref{fig:experiment} summarizes the 
experimental design. We refer the reader to previous QPQ publications for the details on the 
redshift centroiding algorithm, data reduction, and continuum normalization (QPQ6; QPQ8).

@@

\input{Tables/tab_sample.tex}
\input{Tables/tab_summ.tex}
\input{Tables/tab_summ_OIII.tex}

@@

\begin{figure}
\includegraphics[width=3.5in]{Figures/fig_stacks_and_fits.pdf}
\caption{Mean and median absorption centered at \ion{C}{2}\,1334, \ion{C}{4}\,1548, and 
\ion{Mg}{2}\,2796 of the foreground quasars for all QPQ9 pairs. The composites are shown in thick, 
black. Overplotted on the composites are Gaussian fits, normalized to pseudo-continua far away 
from a velocity of $0\,{\rm km\,s^{-1}}$ relative to $z_{\rm fg}$, and are shown in thin, blue. 
For the doublets, a second Gaussian with a fixed mean separation and a tied standard deviation is 
included in the modeling. The absorptions frequently exhibit large velocity widths. The dashed 
lines mark the centroids, which show small positive velocity offsets from $z_{\rm fg}$.  
}
\label{fig:stacks_and_fits}
\end{figure}

@@

[Update the mean and scatter of emission-line redshifts relative to systemic to Shen+16?]

@@

Two results are evident in Figure~\ref{fig:stacks_and_fits}: (i) the mean \ion{C}{2} stack 
exhibits excess absorption spanning a large velocity width; (ii) the mean absorption is skewed 
toward positive velocities. To model the absorption, we introduce a Gaussian profile while 
allowing a constant pseudo-continuum level to vary. From the $\chi^2$ best-fit to the data, 
we measure the centroid of the \ion{C}{2} stack to be $+170\,{\rm km\,s^{-1}}$ and 
the $1\sigma$ dispersion to be $388\,{\rm km\,s^{-1}}$. The centroid suggests an asymmetry that 
contradicts the standard expectation, while the dispersion suggests extreme kinematics. The 
median stack, on the other hand, shows weaker absorption, and the Gaussian model has a centroid 
closer to zero.

@@

@@

\begin{figure*}[!h]
\begin{minipage}[!bp]{0.35\textwidth}
\includegraphics[width=\textwidth]{Figures/fig_stack_z1.pdf}
\caption{Mean stack at \ion{Mg}{2}\,2796, for a lower redshift sample of quasar pairs at 
$z\sim0.9$. Line-style coding is the same as in Figure~\ref{fig:stacks_and_fits}. The centroid is 
approximately $0\,{\rm \,km\,s^{-1}}$, and the absorption is weaker than the main QPQ9 sample. 
}
\label{fig:stack_z1}
\end{minipage}%
\hspace{0.5in}
\begin{minipage}[!bp]{0.55\textwidth}
\includegraphics[width=\textwidth]{Figures/fig_stacks_fg.pdf}
\caption{Mean stacks of the foreground quasar spectra at \ion{C}{2}\,1334, \ion{C}{4}\,1548, and 
\ion{Mg}{2}\,2796 for the QPQ9 sample. For \ion{C}{2} and \ion{Mg}{2}, there is no evidence of 
excess absorption near $z_{\rm fg}$. The stack for \ion{C}{4}, which include line-of-sight 
absorbers at all distances, shows a large, blueshifted mean velocity field.
}
\label{fig:stacks_fg}
\end{minipage}
\end{figure*}

@@

Since \ion{C}{2} systems arise in optically thick absorbers, we may adopt the clustering analysis 
results of QPQ6. In the absence of clustering, the expected number of absorbers per unit redshift 
interval for Lyman limit systems, super Lyman limit systems, and damped Ly$\alpha$ systems are 
respectively $\ell_{\rm IGM}^{\rm LLS}(z)\approx1.05((1+z)/(1+2.5))^{2.1}$, 
$\ell_{\rm IGM}^{\rm SLLS}(z)\approx0.44((1+z)/(1+2.5))^{2.1}$, and 
$\ell_{\rm IGM}^{\rm DLA}(z)\approx0.2((1+z)/(1+2.5))^{2.1}$. The quasar-absorber correlation 
functions for Lyman limit systems, super Lyman limit systems, and damped Ly$\alpha$ systems are 
respectively $\xi_{\rm QA}^{\rm LLS}(r)=(r/(12.5\,h^{-1}\,{\rm Mpc}))^{-1.68}$, 
$\xi_{\rm QA}^{\rm SLLS}(r)=(r/(14.0\,h^{-1}\,{\rm Mpc}))^{-1.68}$, and 
$\xi_{\rm QA}^{\rm DLA}(r)=(r/(3.9\,h^{-1}\,{\rm Mpc}))^{-1.6}$. 
For each quasar pair, we calculate the expected number of all optically thick absorbers within 
$\pm3000\,{\rm km\,s^{-1}}$ at a distance $R_\perp$ from the foreground quasar and at 
$z_{\rm fg}$. Then we generate 1000 mock sightlines. The number of absorbers for each mock 
spectrum is randomly selected from a Poisson distribution with mean equal to the expected number 
calculated as above. The absorbers are randomly assigned Hubble velocities, with a probability 
distribution according to the quasar-absorber correlation functions. The absorbers are randomly 
assigned additional peculiar velocities drawn from a normal distribution with mean equal to 
$0\,{\rm km\,s^{-1}}$ and scatter equal to $\sigma_{\rm 1D}$. For each absorber, we 
assume a rest equivalent width for \ion{C}{2} and a Gaussian absorption profile. We repeat the 
above procedure for all 34 quasar pairs, and create a mean stack of the 34000 mock spectra 
generated. We fit a Gaussian absorption profile multiplied to a constant continuum level to model 
the stack of mock spectra. We adjust the rest equivalent width adopted for the \ion{C}{2} 
absorbers until the ampltiude of the best-fit Gaussian of the stack of mock spectra matches the 
amplitude of the stack of the observational data. We find that a rest equivalent width of 
0.6\,\AA\ well reproduces the amplitude, and the dispersion of the Gaussian absorption model is 
insensitive to the assumed equivalent width or line profile for one absorber. The resulting 
stack of mock spectra has a $1\sigma$ dispersion of $\approx240\,{\rm km\,s^{-1}}$, which is 
smaller than the intrinsic dispersion in the data. We also test for the sensitivity of this 
measured dispersion to the correlation functions adopted. The QPQ6 clustering analysis is 
performed on only the strongest absorber near $z_{\rm fg}$, and a low $R_\perp$ sightline may in 
fact intercept more than one optically thick absorber. We double the number of absorbers for each 
mock sightline, and find the measured dispersion only increases by several ${\rm km\,s^{-1}}$. 
In order to recover an intrinsic dispersion of $317\textendash352\,{\rm km\,s^{-1}}$, a peculiar 
velocity of $\approx280\,{\rm km\,s^{-1}}$ is required. Thus, the observed velocity width is 
indicative of dynamical processes in addition to gravitational motions and Hubble flows.

@@

\begin{figure*}[!h]
\begin{minipage}[!bp]{0.28\textwidth}
\includegraphics[width=\textwidth]{Figures/fig_monopolar.pdf}
\caption{A cartoon showing a unipolar quasar. The gas observed in low- to intermediate-ion 
absorption preferentially lies behind the quasar, and is shadowed from the ionizing radiation. 
}
\label{fig:monopolar}
\end{minipage}%
\hspace{0.3in}
\begin{minipage}[!bp]{0.67\textwidth}
\includegraphics[width=\textwidth]{Figures/fig_lighttravel.pdf}
\caption{A cartoon showing the finite lifetime of quasar episodes as an explanation to the 
asymmetric absorption. The setup on the left shows that the foreground quasar has not been shining 
long enough for its ionizing radiation to reach the gas behind it, when the light from the 
background quasar reaches. The setup on the right shows the scenario after an amount of time 
comparable to the light travelling time across CGM scale. Gas in front of the foreground quasar 
has been ionized, by the time the light from the background quasar reaches. 
}
\label{fig:lighttravel}
\end{minipage}
\end{figure*}

@@

\acknowledgements
[NSF grant number?]

%JXP and MWL acknowledge support from the National
%Science Foundation (NSF) grant AST-1010004 and AST-XX. 
%JXP thanks the Alexander
%von Humboldt foundation for a visitor fellowship to the MPIA where
%part of this work was performed, as well as the staff at MPIA for
%their hospitality during his visits.
%JFH acknowledges generous support from the Alexander von Humboldt
%foundation in the context of the Sofja Kovalevskaja Award. The
%Humboldt foundation is funded by the German Federal Ministry for
%Education and Research.

%Much of the data presented herein were obtained at the W.M. Keck
%Observatory, which is operated as a scientific partnership among the
%California Institute of Technology, the University of California, and
%the National Aeronautics and Space Administration. The Observatory was
%made possible by the generous financial support of the W.M. Keck
%Foundation.  Some of the Keck data were obtained through the NSF
%Telescope System Instrumentation Program (TSIP), supported by AURA
%through the NSF under AURA Cooperative Agreement AST 01-32798 as
%amended.
%
%Some of the data herein were obtained at the Gemini Observatory, which
%is operated by the Association of Universities for Research in
%%Astronomy, Inc., under a cooperative agreement with the NSF on behalf
%of the Gemini partnership: the NSF (United
%States), the Science and Technology Facilities Council (United
%Kingdom), the National Research Council (Canada), CONICYT (Chile), the
%Australian Research Council (Australia), Minist\'{e}rio da
%Ci\^{e}ncia, Tecnologia e Inova\c{c}\~{a}o (Brazil) and Ministerio de
%Ciencia, Tecnolog\'{i}a e Innovaci\'{o}n Productiva (Argentina). 
%
%The authors wish to recognize and acknowledge the very
%significant cultural role and reverence that the summit of Mauna Kea
%has always had within the indigenous Hawaiian community. We are most
%fortunate to have the opportunity to conduct observations from this
%mountain.
%MWL thanks T.-K. Chan for a discussion on CGM simulations. MWL 
%thanks Chi Po Choi for a discussion on statistics.

>>>>

\begin{abstract}
Absorption-line analysis of the circumgalactic medium has traditionally been limited by the 
difficulty to distinguish between inflows and outflows. We examine the flows of gas in the 
environments of massive galaxies hosting quasars at $z\sim2$. We employ 115 projected quasar pairs 
to study the circumgalactic gas of the foreground quasars in absorption. The foreground quasars 
have precise redshift measurements with uncertainty $<400\,{\rm km\,s^{-1}}$. We stack the 
background quasar spectra at the foreground quasar's systemic redshift. The mean absorption in 
\ion{C}{2}, \ion{C}{4}, and \ion{Mg}{2} show large intrinsic velocity fields, and have velocity 
centroids that show a small positive offset relative to the systemic. We argue the results can be 
explained by outflowing gas combined with anisotropic or intermittent ionizing radiation of the 
quasars. 
\end{abstract}

@@

In this paper (hereafter QPQ9), we examine the flows of gas in the environments of massive 
galaxies hosting quasars. Our approach leverages a large dataset of quasar pairs 
\citep[][QPQ1]{QPQ1} to use the 
standard technique of absorption-line spectroscopy with background quasars. These quasar pairs 
have angular separations that correspond to less than 300\,kpc projected separation at the 
foreground quasar's redshift. Our previous publications from these quasar pairs have established 
that these galaxies are surrounded by a massive, cool, and enriched circumgalactic medium 
\citep[QPQ5, QPQ6, QPQ7:][]{QPQ5,QPQ6,QPQ7}. We have collected a sample of 115 background 
spectra that are paired with foreground quasars with precisely measured redshifts. Our primary 
scientific interests are twofold: (i) search for signatures of galactic-scale outflows from the 
central galaxy, presumably driven by recent star formation and/or active galactic nuclei feedback; 
(ii) characterize the dynamics of galactic flows around these massive system. We further describe 
an aspect of this experiment that offers a unique opportunity to study galactic flows: we argue 
that, the anisotropic or intermittent radiation of the foreground quasars breaks the symmetry in 
the velocity field of circumgalactic absorbers.

@@

\input{Tables/tab_sample.tex}
%\input{tab_sample.tex}

\begin{figure}
\includegraphics[width=3in]{Figures/fig_experiment.pdf}
%\includegraphics[width=3in]{f01.pdf}
\caption{These panels summarize properties of the QPQ9 dataset. The QPQ survey selects 
quasar pairs of $R_\perp < 300$\,kpc and $z_{\rm fg}>1.6$. Assuming that the foreground quasars 
emit isotropically and at a distance equal to the impact parameter, the aenhancement in the UV 
flux relative to the extragalactic UV background, $g_{\rm UV}$, can be estimated. Large 
symbols correspond to foreground quasars with the most precise redshift measurement from 
[\ion{O}{3}]\,5007, while small symbols correspond to $z_{\rm fg}$ 
measurements from \ion{Mg}{2}\,2800, H$\alpha$, or H$\beta$ emission. The top panel shows 
quasar pairs with coverage of \ion{C}{2}\,1334 at $z_{\rm fg}$ in the background quasar spectra. 
The middle panel shows pairs with coverage of \ion{C}{4}\,1548. The bottom panel shows 
pairs with coverage of \ion{Mg}{2}\,2796. 
}
\label{fig:experiment}
\end{figure}

@@

From our QPQ survey\footnote{http://www.qpqsurvey.org}, we have analyzed a subset of systems that 
pass within transverse separation $R_\perp<300$\,kpc from a foreground quasar with 
$z_{\rm fg} > 1.6$. We restrict the sample to foreground quasars with redshift measured from 
\ion{Mg}{2}\,2800, [\ion{O}{3}]\,5007, H$\alpha$, or H$\beta$ emission, giving a precision of 
$400\,{\rm km\,s^{-1}}$ or better. 
[\ion{O}{3}] emission-line redshifts have the smallest dispersion of $44\,{\rm km\,s^{-1}}$ about 
the systemic redshift, and we analyze the sub-sample with [\ion{O}{3}] redshifts separately. 
The [\ion{O}{3}] line has an average blueshift of $27\,{\rm km\,s^{-1}}$ about the systemic 
redshift \citep{Boroson05}, which has been added when we compute the 
redshift of the line. Systemic redshifts measured from \ion{Mg}{2} have a precision of 
$272\,{\rm km\,s^{-1}}$, and we have taken into account the median redshift of 
$97\,{\rm km\,s^{-1}}$ of \ion{Mg}{2} from [\ion{O}{3}] \citep{Richards+02}. In QPQ8 
\citep{QPQ8}, we have quantified the precision of H$\alpha$ and H$\beta$ to be 
$300\,{\rm km\,s^{-1}}$ and $392\,{\rm km\,s^{-1}}$ respectively. We further add to the QPQ 
dataset with quasar pairs selected from the public dataset of 
igmspec\footnote{https://github.com/specdb/igmspec}, which includes the spectra from the quasar 
catalogs based upon the Sloan Digital Sky Survey Seventh Data Release \citep{Schneider+10} and the 
Twelfth Data Release \citep{Paris+17}. We 
only select pairs with $z_{\rm fg}$ measured by \cite{HewettWild10} using the \ion{Mg}{2}\,1800 
emission-line. We reached a final sample size of 115. Figure~\ref{fig:experiment} summarizes the 
experimental design. We refer the reader to previous QPQ publications for the details on the 
redshift centroiding algorithm, data reduction, and continuum normalization (QPQ6; QPQ8).

@@

@@

\begin{figure}
\includegraphics[width=3.5in]{Figures/fig_stacks_and_fits.pdf}
%\includegraphics[width=3.5in]{f02.pdf}
\caption{Mean and median absorption centered at \ion{C}{2}\,1334, \ion{C}{4}\,1548, and 
\ion{Mg}{2}\,2796 of the foreground quasars for all QPQ9 pairs. The composites are shown in thick, 
black. Overplotted on the composites are Gaussian fits, normalized to pseudo-continua far away 
from a velocity of $0\,{\rm km\,s^{-1}}$ relative to $z_{\rm fg}$, and are shown in thin, blue. 
For the doublets, a second Gaussian with a fixed mean separation and a tied standard deviation is 
included in the modeling. The absorptions frequently exhibit large velocity widths. The dashed 
lines mark the centroids, which show small positive velocity offsets from $z_{\rm fg}$. The 
$1\sigma$ modeling error of the centroid and dispersion of the \ion{C}{2} mean stack is 
$\approx35\,{\rm km\,s^{-1}}$, which is also the typical modeling errors of the other stacks. 
}
\label{fig:stacks_and_fits}
\end{figure}

@@

%[Update the mean and scatter of emission-line redshifts relative to systemic to Shen+16?]

@@

Two results are evident in Figure~\ref{fig:stacks_and_fits}: (i) the mean \ion{C}{2} stack 
exhibits excess absorption spanning a large velocity width; (ii) the mean absorption is skewed 
toward positive velocities. To model the absorption, we introduce a Gaussian profile while 
allowing a constant pseudo-continuum level to vary. We perform $\chi^2$ minimization with each 
channel by equal weight. From the best-fit to the data, we measure the centroid of the \ion{C}{2} 
stack to be $+170\,{\rm km\,s^{-1}}$ and the $1\sigma$ dispersion to be $388\,{\rm km\,s^{-1}}$. 
The centroid suggests an asymmetry that contradicts the standard expectation, while the dispersion 
suggests extreme kinematics. The median stack, on the other hand, shows weaker absorption, and the 
Gaussian model has a centroid closer to zero.

@@

\input{Tables/tab_summ.tex}
%\input{tab_summ.tex}
\input{Tables/tab_summ_OIII.tex}
%\input{tab_summ_OIII.tex}

\begin{figure*}[!th]
\begin{minipage}[!bp]{0.35\textwidth}
\includegraphics[width=\textwidth]{Figures/fig_stack_z1.pdf}
%\includegraphics[width=\textwidth]{f03.pdf}
\caption{Mean stack at \ion{Mg}{2}\,2796, for a lower redshift sample of quasar pairs at 
$z\sim0.9$. Line-style coding is the same as in Figure~\ref{fig:stacks_and_fits}. The centroid is 
approximately $0\,{\rm \,km\,s^{-1}}$, and the absorption is weaker than the main QPQ9 sample. 
}
\label{fig:stack_z1}
\includegraphics[width=\textwidth]{Figures/fig_monte.pdf}
%\includegraphics[width=\textwidth]{f07.pdf}
\caption{The same \ion{C}{2} mean stack shown in the first panel of 
Figure~\ref{fig:stacks_and_fits} is shown in thick, black, and the Gaussian absorption model to 
the data is shown in thin, blue. In thin, green, we overplot the Gaussian absorption model of the 
Monte Carlo simulations generated from a purely clustering argument. The model from clustering 
analysis is multiplied to the pseudo-continuum level of the stack of the observational data, 
shifted to the centroid of the stack of the data, and broadened by the mean redshift error in the 
data. The model has a smaller dispersion than the data by two times the modeling error.
}
\label{fig:monte}
\end{minipage}%
\hspace{0.5in}
\begin{minipage}[!bp]{0.55\textwidth}
\includegraphics[width=\textwidth]{Figures/fig_stacks_fg.pdf}
%\includegraphics[width=\textwidth]{f04.pdf}
\caption{Mean stacks of the foreground quasar spectra at \ion{C}{2}\,1334, \ion{C}{4}\,1548, and 
\ion{Mg}{2}\,2796 for the QPQ9 sample. For \ion{C}{2} and \ion{Mg}{2}, there is no evidence of 
excess absorption near $z_{\rm fg}$. The stack for \ion{C}{4}, which include line-of-sight 
absorbers at all distances, shows a large, blueshifted mean velocity field.
}
\label{fig:stacks_fg}
\end{minipage}
\end{figure*}

@@

@@

Since \ion{C}{2} systems arise in optically thick absorbers, we may adopt the clustering analysis 
results of QPQ6. In the absence of clustering, the expected number of absorbers per unit redshift 
interval for Lyman limit systems, super Lyman limit systems, and damped Ly$\alpha$ systems are 
respectively $\ell_{\rm IGM}^{\rm LLS}(z)\approx1.05((1+z)/(1+2.5))^{2.1}$, 
$\ell_{\rm IGM}^{\rm SLLS}(z)\approx0.44((1+z)/(1+2.5))^{2.1}$, and 
$\ell_{\rm IGM}^{\rm DLA}(z)\approx0.2((1+z)/(1+2.5))^{2.1}$. The quasar-absorber correlation 
functions for Lyman limit systems, super Lyman limit systems, and damped Ly$\alpha$ systems are 
respectively $\xi_{\rm QA}^{\rm LLS}(r)=(r/(12.5\,h^{-1}\,{\rm Mpc}))^{-1.68}$, 
$\xi_{\rm QA}^{\rm SLLS}(r)=(r/(14.0\,h^{-1}\,{\rm Mpc}))^{-1.68}$, and 
$\xi_{\rm QA}^{\rm DLA}(r)=(r/(3.9\,h^{-1}\,{\rm Mpc}))^{-1.6}$. 
For each quasar pair, we calculate the expected number of all optically thick absorbers within 
$\pm3000\,{\rm km\,s^{-1}}$ at a distance $R_\perp$ from the foreground quasar and at 
$z_{\rm fg}$. Then we generate 1000 mock sightlines. The number of absorbers for each mock 
spectrum is randomly selected from a Poisson distribution with mean equal to the expected number 
calculated as above. The absorbers are randomly assigned Hubble velocities, with a probability 
distribution according to the quasar-absorber correlation functions. The absorbers are randomly 
assigned additional peculiar velocities drawn from a normal distribution with mean equal to 
$0\,{\rm km\,s^{-1}}$ and scatter equal to $\sigma_{\rm 1D}$. For each absorber, we 
assume a rest equivalent width for \ion{C}{2} and a Gaussian absorption profile. We repeat the 
above procedure for all 34 quasar pairs, and create a mean stack of the 34000 mock spectra 
generated. We fit a Gaussian absorption profile multiplied to a constant continuum level to model 
the stack of mock spectra. We adjust the rest equivalent width adopted for the \ion{C}{2} 
absorbers until the ampltiude of the best-fit Gaussian of the stack of mock spectra matches the 
amplitude of the stack of the observational data. We find that a rest equivalent width of 
0.6\,\AA\ well reproduces the amplitude, and the dispersion of the Gaussian absorption model is 
insensitive to the assumed equivalent width or line profile for one absorber. In 
Figure~\ref{fig:monte}, we show a comparison of the observational data stack and the Gaussian 
absorption model of the Monte Carlo simulations. In the figure, the Gaussian absorption model is 
broadened by the mean redshift error by adding it in quadrature to the dispersion in the model. 
The resulting stack of mock spectra has a $1\sigma$ dispersion of $\approx240\,{\rm km\,s^{-1}}$, 
which is smaller than the intrinsic dispersion in the data by two times the $1\sigma$ modeling 
error. We also test for the sensitivity of this 
measured dispersion to the correlation functions adopted. The QPQ6 clustering analysis is 
performed on only the strongest absorber near $z_{\rm fg}$, and a low $R_\perp$ sightline may in 
fact intercept more than one optically thick absorber. We double the number of absorbers for each 
mock sightline, and find the measured dispersion only increases by several ${\rm km\,s^{-1}}$. 
In order to recover an intrinsic dispersion of $317\textendash352\,{\rm km\,s^{-1}}$, a peculiar 
velocity of $\approx280\,{\rm km\,s^{-1}}$ is required. Thus, the observed velocity width suggests 
a hint of dynamical processes in addition to gravitational motions and Hubble flows.

@@

\begin{figure*}[!th]
\begin{minipage}[!bp]{0.28\textwidth}
\includegraphics[width=\textwidth]{Figures/fig_monopolar.pdf}
%\includegrpahics[width=\textwidth]{f05.pdf}
\caption{A cartoon showing a unipolar quasar. The gas observed in low- to intermediate-ion 
absorption preferentially lies behind the quasar, and is shadowed from the ionizing radiation. 
}
\label{fig:monopolar}
\end{minipage}%
\hspace{0.3in}
\begin{minipage}[!bp]{0.67\textwidth}
\includegraphics[width=\textwidth]{Figures/fig_lighttravel.pdf}
%\includegraphics[width=\textwidth]{f06.pdf}
\caption{A cartoon showing the finite lifetime of quasar episodes as an explanation to the 
asymmetric absorption. The setup on the left shows that the foreground quasar has not been shining 
long enough for its ionizing radiation to reach the gas behind it, when the light from the 
background quasar reaches. The setup on the right shows the scenario after an amount of time 
comparable to the light travelling time across CGM scale. Gas in front of the foreground quasar 
has been ionized, by the time the light from the background quasar reaches. 
}
\label{fig:lighttravel}
\end{minipage}
\end{figure*}

@@

\acknowledgements

JXP and MWL acknowledge support from the National Science Foundation (NSF) grants AST-1412981. The 
authors gratefully acknowledge the support which enabled these observations at the Keck, Gemini, 
Large Binocular Telescope, Very Large Telescope, Las Campanas, and Palomar Observatories. MWL 
thanks T.-K. Chan for a discussion on CGM simulations and Chi Po Choi for a discussion on 
statistics.
